Forecasting Gamma-Ray Bursts using Gravitational Waves

### 2018-11-21 Paper/Manuscript.tex
finished the Mathematica

\todo{1) See end of Sec. IV on page 13, 2) Finish new Sec VIII on BH-BH inspirals, 3) page 19. footnote}
\end{abstract}
\maketitle

@@

100 &   28.2\,minutes & 503 &{\qquad} &  2.15\,hours & 601\T\\
200 & 8.21\,minutes & 251  &{\qquad} & 1.10\,hours & 300 \\
400 &  2.00\,minutes & 124 &{\qquad} & 34.2\,minutes & 148\\
1000 & 14.3\,seconds & 49 &{\qquad} & 13.9\,minutes& 58.5\\
\hline\hline
%bottomrule
\end{tabular}
\caption{Same as Table~\ref{table:ET}, but now for a $5 M_\odot- 1.4 M_\odot$ black hole-neutron star binary.
The SNRs are even higher than before, however the advance warning times have decreased significantly.}\label{table:ET_BH_NS}
\end{table}
%
%

From the table, we can see that the range of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
there could be $\approx 30$ such mergers per year within ET-C's range of $\approx 200\,$Mpc. %corresponding roughly to $T_\text{AW}\approx1\,$hour.
We must emphasize that this should be viewed
as an upper limit as low-mass, high-spin black holes such as ours above are expected to be rare.
Theoretical studies indicate that $\lesssim 10\%$ stellar-mass BHs have masses $\lesssim 5 M_\odot$ \cite{Fryer:1999ht}.
This seems to be supported at least by observations of galactic black holes \cite{Ozel:2010su}.
Therefore, we realistically expect ET-C to forecast $\lesssim 3$ tidal disruption events per year.
%A better estimation would need to incorporate the percentage of such black holes from population studies and Monte-Carlo simulations,
%however, all of these come with rather large error bars.
%and that no TD occurs for $a=0$. This is roughly consistent with Fig.5 of Ref.~\cite{Hanna:2008um}
%Choosing lower mass implies reduced SNR since $\rho \propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$,
%but even with $m_2=5 M_\odot$, a BH-NS binary is ``louder'' than a BNS system at the same distance. 
%and as we showed in Sec.~\ref{sec:results}, low SNR is not going to be a problem with ET sensitivities out to $D \sim 1\,$Gpc.
%
%It is straightforward to show that this mass bound is only consistent with spinning black holes by substituting the naive Schwarzschild $r_\text{ISCO}$ value 
%into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.
%ISCO location from NR 
%\be
%\Omega_\text{ISCO} M = 0.068 \left[ 1- \f{0.444}{Q^{1/4}}(1-3.54 C^{1/3})\right] 
%\ee
%
\section{Bnary black hole inspirals}\label{sec:BH_BH}
We briefly repeat our computations for binary black hole (BBH) inspirals.
As it is clear that heavier systems inspiral too fast, we limit ourselves
to $5M_\odot-5M_\odot$ BBHs and only consider ET-C.
\todo{Finish this}

>>>>

\todo{1) See end of Sec. IV on page 13, 2) Finish new Sec VIII on BH-BH inspirals, 3) page 19. footnote, 4) fix TAble VI}
\end{abstract}
\maketitle

@@

100 &   28.2\,minutes & 503 &{\qquad} &  2.15\,hours & 601\T\\
200 & 8.21\,minutes & 251  &{\qquad} & 1.10\,hours & 300 \\
400 &  2.00\,minutes & 124 &{\qquad} & 34.2\,minutes & 148\\
1000 & 14.3\,seconds & 49 &{\qquad} & 13.9\,minutes& 58.5\\
\hline\hline
%bottomrule
\end{tabular}
\caption{\todo{FIX these numbers}Same as Table~\ref{table:ET}, but now for a $5 M_\odot- 1.4 M_\odot$ black hole-neutron star binary.
The SNRs are even higher than before, however the advance warning times have decreased significantly.}\label{table:ET_BH_NS}
\end{table}
%
%

From the table, we can see that the range of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
there could be $\approx 30$ such mergers per year within ET-C's range of $\approx 200\,$Mpc. %corresponding roughly to $T_\text{AW}\approx1\,$hour.
We must emphasize that this should be viewed
as an upper limit as low-mass, high-spin black holes such as ours above are expected to be rare.
Theoretical studies indicate that $\lesssim 10\%$ stellar-mass BHs have masses $\lesssim 5 M_\odot$ \cite{Fryer:1999ht}.
This seems to be supported at least by observations of galactic black holes \cite{Ozel:2010su}.
Therefore, we realistically expect ET-C to forecast $\lesssim 3$ tidal disruption events per year.
%A better estimation would need to incorporate the percentage of such black holes from population studies and Monte-Carlo simulations,
%however, all of these come with rather large error bars.
%and that no TD occurs for $a=0$. This is roughly consistent with Fig.5 of Ref.~\cite{Hanna:2008um}
%Choosing lower mass implies reduced SNR since $\rho \propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$,
%but even with $m_2=5 M_\odot$, a BH-NS binary is ``louder'' than a BNS system at the same distance. 
%and as we showed in Sec.~\ref{sec:results}, low SNR is not going to be a problem with ET sensitivities out to $D \sim 1\,$Gpc.
%
%It is straightforward to show that this mass bound is only consistent with spinning black holes by substituting the naive Schwarzschild $r_\text{ISCO}$ value 
%into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.
%ISCO location from NR 
%\be
%\Omega_\text{ISCO} M = 0.068 \left[ 1- \f{0.444}{Q^{1/4}}(1-3.54 C^{1/3})\right] 
%\ee
%
\section{Bnary black hole inspirals}\label{sec:BH_BH}
We briefly repeat our computations for binary black hole (BBH) inspirals.
As heavier systems inspiral too fast, we limit ourselves
to $5M_\odot-5M_\odot$ BBHs and only consider ET-C.
For these systems, we find that $T_\text{AW} \lesssim 1\,$hour for $D\gtrsim 190\,$Mpc, but $\bar{\rho}_F$ will exceed 500. As such lightweight black holes
are expected to be rare and given the BBH merger rate inferred from the previous LIGO detections \todo{FInd the event rate}, we expect no forecasts
for these events. Nonetheless, ET will detect hundreds to thousands of BBH mergers.
